%
% File: chap01.tex
% Author: Victor F. Brena-Medina
% Description: Introduction chapter where the biology goes.
%
\let\textcircled=\pgftextcircled
\chapter{Conclusions}
\label{chap:conclusion}

This chapter gives a brief of the research work carried out and the conclusions drawn from the same. The future work is also discussed in this chapter.

\section{Conclusion}
\paragraph{}

The problem regarding the Von-Neumann bottleneck as discussed before is substantial specially when dealing with data intensive tasks. The In-Memory computing paradigm that has been explored in this project is one of the promising ways to overcome the hurdle of time, power and chip area consumption in today's scenario when the Moore's law is at it's saturation.  

In this project, we have looked towards logical operations without logical gates, binary shift without flip flops. These optimizations have led to decrease in area, time and power which is essential for In-Memory Computation. The idea to simulate and perform tasks with the architecture using Assembly code eases the usability and makes it more friendly to use. This feature will play a key role once such a fabricated chip has to be programmed. 

Thus, In-Memory Computation will pave way for faster and power efficient processing specially data intensive tasks and a continued research in this field will surely bring such hardware in the hands of the people sooner.    

 
\section{Scope for Future Research}
\paragraph{}

The future research in this area can be in the following directions:

\begin{itemize}

\item Developing complex arithmetic operations like multiplication and division on floating point numbers and Extending the instruction set to perform more variety of tasks

\item Designing the architecture for Low Power purposes for the use in fields like IOT.

\item Improving upon the delay, area and power consumption by using lower technology nodes having lesser parasitics.

\item Improving the design for wider memory bandwidth to meet the current data intensive computational needs.
\end{itemize}
 